---
title: "Analysis_mod_MSE"
author: "Sophia Kleist Karlson"
date: "22 nov 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



Mod 3: Error between images


```{r}

setwd("~/Social Transmission Study/Analysis of drawings/")
pacman::p_load(tidyverse, brms, ggplot2, stringr, dplyr)

RStudio.Version()

data_MSE <- read_csv("data/csv_files/all_data_w_MSE.csv") #we use all_data_w_MSE.csv
data_MSE$X1 <- NULL#removing the first unnecessary column

```

Preparing the data and checking stuff
```{r}
# Checking classes

# Generation and MSE should be numeric
class(data_MSE$Generation)
class(data_MSE$MSE)

# Subject and Drawing ID should be character
class(data_MSE$Subject)
class(data_MSE$Drawing_ID)

# Chain, condition and Source_image should be factors
class(data_MSE$Chain)
class(data_MSE$Condition)
class(data_MSE$Source_image)

data_MSE$Chain <- as.factor(data_MSE$Chain)
data_MSE$Condition <- as.factor(data_MSE$Condition)
data_MSE$Source_image <- as.factor(data_MSE$Source_image)


# Chose the variables needed for the model
df_MSE <- data_MSE %>% select(Subject, Chain, Generation, Condition, Source_image, MSE)

```


some plots
```{r}
# we make condition into numeric for the plots
class(df_MSE$Condition)
df_MSE$Condition <- as.numeric(df_MSE$Condition)

class(df_MSE$MSE)

range(df_MSE$MSE)
mean(df_MSE$MSE)#9427.756
sd(df_MSE$MSE)#2412.739

# conditions and conventionality
plot_simple_cond <- ggplot(df_MSE, aes(Condition, MSE)) +
                             geom_jitter()#geom_smooth(method = lm)#geom_jitter()#geom_bar(stat = "identity")
plot_simple_cond

# generation and conventionality
plot_simple_gen <- ggplot(df_MSE, aes(Generation, MSE)) +
  geom_bar(stat = "identity")
  #geom_smooth(method = lm)
plot_simple_gen




# generation, condition and conventionality
df_MSE$Condition <- as.factor(df_MSE$Condition)

plot_simple_gen_cond <- ggplot(df_MSE, aes(Generation, MSE, color = Condition)) +
                             geom_smooth(method = lm)
plot_simple_gen_cond



df_MSE$Generation <- as.factor(df_MSE$Generation)


plot_simple_gen_cond1 <- ggplot(subset(df_MSE, Condition == 1), aes(Generation, MSE)) +
                             geom_bar(stat = "identity")
plot_simple_gen_cond1

plot_simple_gen_cond2 <- ggplot(subset(df_MSE, Condition == 2), aes(Generation, MSE)) +
                             geom_bar(stat = "identity")
plot_simple_gen_cond2

plot_simple_gen_cond3 <- ggplot(subset(df_MSE, Condition == 3), aes(Generation, MSE)) +
                             geom_bar(stat = "identity")

plot_simple_gen_cond3


plot_simple_gen_cond4 <- ggplot(subset(df_MSE, Condition == 4), aes(Generation, MSE)) +
                             geom_bar(stat = "identity")
plot_simple_gen_cond4




# source image and conventionality
plot_simple_gen_source <- ggplot(df_MSE, aes(Source_image, MSE)) +
  geom_bar(stat = "identity")# +
  #geom_errorbar(aes(ymin=(Complexity-sd(Complexity)), ymax=(Complexity-sd(Complexity))), width=.2, position=position_dodge(.9))
plot_simple_gen_source

# participant and conventionality
plot_simple_subj <- ggplot(df_MSE, aes(Subject, MSE)) +
                            geom_jitter()#geom_bar(stat = "identity")
plot_simple_subj

```


Ideal model: 

Complexity ~ 1 + Condition*Generation +
  (1 + condition*generation | Source_image) +
  (1 + condition*generation | Subject:Chain) +
  (1 + condition*generation | Chain)


simple model, with no bayesian fansy
```{r}
pacman::p_load(lmerTest, ggplot2)

simple_mod_MSE_1 <- lm(MSE ~ 1 + Condition, df_MSE)
summary(simple_mod_MSE_1)

simple_mod_MSE_2 <- lm(MSE ~ 1 + Generation, df_MSE)
summary(simple_mod_MSE_2) # there is a small rise in conventionality through generations across conditions

simple_mod_MSE_3 <- lm(MSE ~ 1 + Generation*Condition, df_MSE)
summary(simple_mod_MSE_3) # I'm a bit confused by these results


simple_mod_MSE_4 <- lmerTest::lmer(MSE ~ 1 + Condition + (1 + Condition | Subject), df_MSE) # failed to converge
summary(simple_mod_MSE_4)

simple_mod_MSE_5 <- lmerTest::lmer(MSE ~ 1 + Generation + (1 + Generation | Subject), df_MSE)# boundary singular fit and failed to converge
summary(simple_mod_MSE_5)


simple_mod_MSE_6 <- lmerTest::lmer(MSE ~ 1 + Condition + Generation + 
                       (1 + Condition + Generation | Subject), df_MSE)
summary(simple_mod_MSE_6)

simple_mod_MSE_7 <- lmerTest::lmer(MSE ~ 1 + Generation*Condition + (1 + Generation*Condition | Subject), df_MSE)
summary(simple_mod_MSE_7)
```

lmer(formula, data = NULL, REML = TRUE, control = lmerControl(),
     start = NULL, verbose = 0L, subset, weights, na.action,
     offset, contrasts = NULL, devFunOnly = FALSE)

mod_f1_2 <- lmerTest::lmer(yi ~ 1 + (1 | studyID), es_f1_2, weights = 1/vi, REML=F, control = lme4::lmerControl( check.nobs.vs.nlev ='ignore', check.nobs.vs.nRE = 'ignore'))
summary(mod_f1_2) # We get boundary (singular) fit again. Ouch. Does it matter? WHo knows. Maybe Riccardo does.





Modeling
```{r}
# Set seed so that the analysis can be re-run and give the same results
set.seed(555)

# Define the model
MSE_mod <- bf(MSE ~ 1 + Condition + Generation + Condition:Generation) #+ 
                       #(1 + Condition + Generation + Condition:Generation | Subject)) #+
                       #(1 + Condition + Generation + Condition:Generation | Source_image))


# Figure out what priors we'll need
get_prior(MSE_mod, family = gaussian, df_MSE)

# Checking range, mean and standard deviation of complexity, to determine which family to choose and to use for beta- and intercept-priors
range(df_MSE$MSE)
mean(df_MSE$MSE)
sd(df_MSE$MSE)

# For choosing the sd prior - GROUP BY DRAWING AND NOT SUBJECT???
df_part <- df_MSE %>% group_by(Subject) %>% summarize(mean_MSE = mean(MSE)) #find mean complexity for each participant
sd(df_part$mean_MSE)/2 #get the standard deviation of the mean complexity for each participant. Divide this in two


prior_MSE_mod <- c(
  prior(normal(4.38, 2.81),     class = b), #mean and sd of Conventionality
  #prior(lkj(1),                        class = cor),
  prior(normal(4.38, 2.81),     class = Intercept), #mean and sd of Conventionality
  #prior(normal(0, 1390.23),            class = sd), #mean: 0 (I expect that they might not vary at all). sd for the mean complexity for each participant = 2780.45. sigma should go from 0 (the mean of the prior) to around that -> sigma: 1390.23.
  prior(normal(2.81, 1.40),      class = sigma) #mean: sd of Conventionality. sigma: half of the sd of Conventionality
)


# Running the model to check priors
MSE_mod0 <- brm(
  formula = MSE_mod, 
  prior = prior_MSE_mod,
  data = df_MSE,
  chains = 2,
  cores = 2,
  sample_prior = "only"
)


# Prior predictive check
pp_check(MSE_mod0, nsamples = 100) # 


# The actual model:
MSE_mod1 <- brm(
  formula = MSE_mod, 
  prior = prior_MSE_mod,
  data = df_MSE,
  chains = 2,
  cores = 2,
  sample_prior = T,
  iter = 4000,
  control = list(adapt_delta=0.99, max_treedepth=20)
)

# Posterior predictive check
pp_check(MSE_mod1, nsamples = 100)



# Model summary
summary(MSE_mod1) # Warnings? Suspicious Rhat activity? Bad priors?

# Plot the model to get trace plots
plot(MSE_mod1)


# Rank trace plots
mcmc_rank_overlay(MSE_mod1, 
                  pars = c("b_Intercept", "b_Condition2", "b_Condition3", "b_Condition4")) + 
  theme_classic()

mcmc_rank_overlay(MSE_mod1, 
                  pars = c("b_Generation", "b_Condition2:Generation", "b_Condition3:Generation", "b_Condition4:Generation")) + 
  theme_classic()

mcmc_rank_overlay(MSE_mod1, 
                  pars = c("sigma")) + 
  theme_classic()




hypothesis(MSE_mod1,"Condition2 = Condition3") # Is condition 2 more complex than condition 3?
hypothesis(MSE_mod1,"Condition3 = Condition4")
hypothesis(MSE_mod1,"Condition2 = Condition4")

hypothesis(MSE_mod1,"Intercept > 0")

hypothesis(MSE_mod1,"Generation = 0") # this is the most probable in terms of generation
hypothesis(MSE_mod1,"Condition2:Generation > 0") # this is more probable than =, and a LOT more than <
hypothesis(MSE_mod1,"Condition3:Generation > 0") # this is more probable than =, and a LOT more than <
hypothesis(MSE_mod1,"Condition4:Generation > 0") # this is more probable than =, and a LOT more than <

plot(hypothesis(MSE_mod1, "")) # After trying different hypotheses, this turned out to be the best


# Plot conditional effects
conditional_effects(MSE_mod1)
```




