---
title: "Other_models"
author: "Sophia Kleist Karlson"
date: "4 dec 2020"
output: html_document
---


```{r}
# set working directory
setwd("~/Social Transmission Study/Analysis of drawings/")

# load necesary packages through pacman
pacman::p_load(tidyverse, brms, ggplot2, stringr, dplyr)

# RStudio version
RStudio.Version()

# read data and delete the first unnecessary column
data_conv <- read_csv("data/csv_files/all_data_w_all_conv_source.csv") #we use all_data_w_all_conv_source.csv
data_conv$X1 <- NULL

```



simple model, with no bayesian fansy
```{r}
pacman::p_load(lmerTest, ggplot2)

simple_mod_conv_1 <- lm(Conventionality ~ 1 + Condition, df_conventionality)
summary(simple_mod_conv_1)

simple_mod_conv_2 <- lm(Conventionality ~ 1 + Generation, df_conventionality)
summary(simple_mod_conv_2) # there is a small rise in conventionality through generations across conditions

simple_mod_conv_3 <- lm(Conventionality ~ 1 + Generation*Condition, df_conventionality)
summary(simple_mod_conv_3) # I'm a bit confused by these results


simple_mod_conv_4 <- lmerTest::lmer(Conventionality ~ 1 + Condition + (1 + Condition | Subject), df_conventionality) # failed to converge
summary(simple_mod_conv_4)

simple_mod_conv_5 <- lmerTest::lmer(Conventionality ~ 1 + Generation + (1 + Generation | Subject), df_conventionality)# boundary singular fit and failed to converge
summary(simple_mod_conv_5)


simple_mod_conv_6 <- lmerTest::lmer(Conventionality ~ 1 + Condition + Generation + 
                       (1 + Condition + Generation | Subject), df_conventionality)
summary(simple_mod_conv_6)

simple_mod_conv_7 <- lmerTest::lmer(Conventionality ~ 1 + Generation*Condition + (1 + Generation*Condition | Subject), df_conventionality)
summary(simple_mod_conv_7)
```

lmer(formula, data = NULL, REML = TRUE, control = lmerControl(),
     start = NULL, verbose = 0L, subset, weights, na.action,
     offset, contrasts = NULL, devFunOnly = FALSE)

mod_f1_2 <- lmerTest::lmer(yi ~ 1 + (1 | studyID), es_f1_2, weights = 1/vi, REML=F, control = lme4::lmerControl( check.nobs.vs.nlev ='ignore', check.nobs.vs.nRE = 'ignore'))
summary(mod_f1_2) # We get boundary (singular) fit again. Ouch. Does it matter? WHo knows. Maybe Riccardo does.