---
title: "Plotting and inspecting data"
author: "Sophia Kleist Karlson"
date: "4 dec 2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# load necesary packages through pacman
pacman::p_load(tidyverse, ggplot2)

# set working directory
setwd("~/Social Transmission Study/Analysis of drawings/")

# RStudio version
RStudio.Version()

# read data and delete the first unnecessary column
data <- read_csv("data/csv_files/all_data_w_all_conv_source.csv") #we use all_data_w_all_conv_source.csv
data$X1 <- NULL
```


Plotting 

I chose to make two barplots with the standard error as errorbars. Each plot shows the generation on the x-axis (from 0-7, 0 being the source images) and either the complexity or conventionality scores on the y-axis. For each generation, four bars represent each condition, color-coded as shown in the legend to the right of the plot.

```{r}

# Read data into R if you have cleaned the environment
#all_data_w_all_conv_source <- read.csv("data/csv_files/all_data_w_all_conv_source.csv")

# check classes of the variables of interest
class(data$Condition)
class(data$Generation)
class(data$Conventionality)
class(data$Complexity)

# change class for generation and condition to factor, and complexity and conventionality to numeric
data$Condition <- as.factor(data$Condition)
data$Generation <- as.factor(data$Generation)
data$Conventionality <- as.numeric(data$Conventionality)
data$Complexity <- as.numeric(data$Complexity)

# check range, mean and sd of conventionality and complexity
range(data$Conventionality) # 0-10
mean(data$Conventionality) # 4.33
sd(data$Conventionality) # 2.80

range(data$Complexity) # 4287-50067
mean(data$Complexity) # 24641.25
sd(data$Complexity) # 6399.96


# plotting complexity 
complexity_plot <- ggplot(data, aes(Generation, Complexity, fill = Condition)) +
  geom_bar(fun.y = "mean", stat = "summary", position = "dodge") +
  ggtitle("Development of complexity") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge")

complexity_plot

# plotting conventionality 
conventionality_plot <- ggplot(data, aes(Generation, Conventionality, fill = Condition)) +
  geom_bar(fun.y = "mean", stat = "summary", position = "dodge") +
  ggtitle("Development of conventionality") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge")

conventionality_plot


# plotting complexity across chains
complexity_plot <- ggplot(data, aes(Generation, Complexity, fill = Condition)) +
  geom_bar(fun.y = "mean", stat = "summary", position = "dodge") +
  ggtitle("Development of complexity") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge") +
  facet_wrap(data$Chain)

complexity_plot

# plotting conventionality across chains
conventionality_plot <- ggplot(data, aes(Generation, Conventionality, fill = Condition)) +
  geom_bar(fun.y = "mean", stat = "summary", position = "dodge") +
  ggtitle("Development of conventionality") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge") +
  facet_wrap(data$Chain)

conventionality_plot


```




looking at mean and sd of the data in different ways
```{r}
all_data_m1 <- data.frame(matrix(ncol = 1, nrow = 0)) #ncol doesn't actually make a difference

for (i in 1:length(list_files_m)){
  file_path_m <- list_files_m[i]
  d_m <- jsonlite::fromJSON(file_path_m, flatten=T) %>% 
    #select(drawing_id, button_pressed, completion_code) %>% 
    rename(Drawing_ID = drawing_id,
           Conventionality = button_pressed) %>% 
    filter(is.na(Drawing_ID) + is.na(completion_code) < 2 ,)
  if (nrow(all_data_m1) == 0){
    all_data_m1 <- d_m
  } else {
    all_data_m1 <- rbind(all_data_m1, d_m)
  }
}

all_data_m1$Conventionality <- as.numeric(all_data_m1$Conventionality)
class(all_data_m1$Conventionality)


# grouping by participant and looking at the last 35 images
conv_last35 <- all_data_m1 %>% 
  group_by(subject) %>%   
  slice(tail(row_number(), 35)) %>% 
  select(Conventionality, subject) %>% 
  as.data.frame()

mean(conv_last35$Conventionality) #4.606845 - so basically the same as the overall mean
sd(conv_last35$Conventionality) #2.965397 - also basically the same - both mean and sd go up 0.1 but it doesn't seem problematic


# grouping by participant
conv_by_subject <- all_data_m1 %>% 
  group_by(subject) %>%
  select(Conventionality, subject) %>% 
  summarise(mean(Conventionality), sd(Conventionality)) %>% 
  as.data.frame()

conv_by_subject

range(conv_by_subject[,3]) #range of sd's of scores for each image goes from 0.6206257 to 3.9582781 - people are generally rating images higher than others are
mean(conv_by_subject[,3]) # mean sd og each participant is 2.087293, so they each are relatively stable in their trend


# grouping by image
conv_by_image <- all_data_m1 %>% 
  group_by(Drawing_ID) %>%   
  select(Conventionality, Drawing_ID) %>% 
  summarise(mean(Conventionality), sd(Conventionality)) %>% 
  as.data.frame()


conv_by_image <- conv_by_image[-c(1693), ] # deleitng the empty row (don't know where it came from, but it's all empty)

range(conv_by_image[,3]) #range of sd's of scores for each image goes from 0.834523 to 4.274091 - so for some images, people are not agreeing, for others, they are 
mean(conv_by_image[,3]) # mean sd of each image is 2.723376, so around the same as the overall sd

```



# looking at sd
```{r}

gen_0_cond_1 <- df_conventionality %>% subset(Generation == 0 & Condition == 1)
mean(gen_0_cond_1$Conventionality)
sd(gen_0_cond_1$Conventionality)

gen_0_cond_2 <- df_conventionality %>% subset(Generation == 0 & Condition == 2)
mean(gen_0_cond_2$Conventionality)
sd(gen_0_cond_2$Conventionality)

gen_0_cond_3 <- df_conventionality %>% subset(Generation == 0 & Condition == 3)
mean(gen_0_cond_3$Conventionality)
sd(gen_0_cond_3$Conventionality)

gen_0_cond_4 <- df_conventionality %>% subset(Generation == 0 & Condition == 4)
mean(gen_0_cond_4$Conventionality)
sd(gen_0_cond_4$Conventionality)


gen_1_cond_1 <- df_conventionality %>% subset(Generation == 1 & Condition == 1)
mean(gen_1_cond_1$Conventionality)
sd(gen_1_cond_1$Conventionality)

gen_1_cond_2 <- df_conventionality %>% subset(Generation == 1 & Condition == 2)
mean(gen_1_cond_2$Conventionality)
sd(gen_1_cond_2$Conventionality)

gen_1_cond_3 <- df_conventionality %>% subset(Generation == 1 & Condition == 3)
mean(gen_1_cond_3$Conventionality)
sd(gen_1_cond_3$Conventionality)

gen_1_cond_4 <- df_conventionality %>% subset(Generation == 1 & Condition == 4)
mean(gen_1_cond_4$Conventionality)
sd(gen_1_cond_4$Conventionality)
```


some plots
```{r}

p_load(ggplot2, tidyr, dplyr)

class(df_conventionality$Condition)
class(df_conventionality$Generation)
class(df_conventionality$Conventionality)

df_conventionality$Condition <- as.factor(df_conventionality$Condition)


range(df_conventionality$Conventionality)
mean(df_conventionality$Conventionality)#4.38
sd(df_conventionality$Conventionality)#2.81

# conditions and conventionality
plot_simple_cond <- ggplot(df_conventionality, aes(Condition, Conventionality)) +
                             #geom_smooth(method = lm)#
  geom_jitter()#geom_bar(stat = "identity")
plot_simple_cond

# generation and conventionality
plot_simple_gen <- ggplot(df_conventionality, aes(Generation, Conventionality)) +
  geom_bar(stat = "identity")
  #geom_smooth(method = lm)
plot_simple_gen




# generation, condition and conventionality
class(df_conventionality$Condition)
class(df_conventionality$Generation)
class(df_conventionality$Conventionality)

df_conventionality$Condition <- as.factor(df_conventionality$Condition)
df_conventionality$Condition <- as.character(df_conventionality$Condition)
df_conventionality$Condition <- as.numeric(df_conventionality$Condition)

df_conventionality$Generation <- as.factor(df_conventionality$Generation)
df_conventionality$Generation <- as.character(df_conventionality$Generation)
df_conventionality$Generation <- as.numeric(df_conventionality$Generation)





# make dataset for plots where sd for complexity and convenionality for each condition in each generation is made into a seperate row
sd(all_data_w_all_conv_source$Conventionality)


SD <- all_data_w_all_conv_source %>% group_by(Generation, Condition) %>% mutate(SD_compl = sd(Complexity), SD_conv = sd(Conventionality)) %>% select(Chain, Generation, Condition, Complexity, Conventionality, SD_compl, SD_conv)

SD %>%
    group_by(Generation, Condition) %>%
    summarise(conv.mean = mean(Conventionality), conv.sd = sd(Conventionality)) %>%
    ggplot(aes(Generation, conv.mean, fill = Condition)) +
    geom_col(position = position_dodge(width = 0.8)) +
    geom_errorbar(
        aes(ymin = conv.mean - conv.sd, ymax = conv.mean + conv.sd),
        position = position_dodge(width = 0.8),
        width = 0.2)

SD_chain <- SD %>% 
    group_by(Generation, Condition, Chain) %>%
    summarise(conv.mean = mean(Conventionality), conv.sd = sd(Conventionality), 
              conv.se = sd(Conventionality)/sqrt(16), 
              comp.mean = mean(Complexity), comp.sd = sd(Complexity), 
              comp.se = sd(Complexity)/sqrt(16)) 


SD_1 <- all_data_w_all_conv_source %>% 
    group_by(Generation, Condition) %>%
    summarise(conv.mean = mean(Conventionality), conv.sd = sd(Conventionality), 
              conv.se = sd(Conventionality)/sqrt(320),
              comp.mean = mean(Complexity), comp.sd = sd(Complexity), 
              comp.se = sd(Complexity)/sqrt(320)) 


ggplot(SD_chain, aes(Generation, conv.mean, fill = Condition)) +
    geom_col(position = position_dodge(width = 0.8)) +
    geom_errorbar(
        aes(ymin = conv.mean - conv.se, ymax = conv.mean + conv.se),
        position = position_dodge(width = 0.8),
        width = 0.2) +
    facet_wrap(SD_chain$Chain)

ggplot(SD_1, aes(Generation, conv.mean, fill = Condition)) +
    geom_col(position = position_dodge(width = 0.8)) +
    geom_errorbar(
        aes(ymin = conv.mean - conv.se, ymax = conv.mean + conv.se),
        position = position_dodge(width = 0.8),
        width = 0.2)


ggplot(SD_chain, aes(Generation, comp.mean, fill = Condition)) +
    geom_col(position = position_dodge(width = 0.8)) +
    geom_errorbar(
        aes(ymin = comp.mean - comp.se, ymax = comp.mean + comp.se),
        position = position_dodge(width = 0.8),
        width = 0.2) +
    facet_wrap(SD_chain$Chain)

ggplot(SD_1, aes(Generation, comp.mean, fill = Condition)) +
    geom_col(position = position_dodge(width = 0.8)) +
    geom_errorbar(
        aes(ymin = comp.mean - comp.se, ymax = comp.mean + comp.se),
        position = position_dodge(width = 0.8),
        width = 0.2)


plot_simple_gen_cond <- ggplot(SD, aes(Generation, Conventionality, fill = Condition)) +
  geom_bar(fun.y = "mean", stat = "summary", position = "dodge") +
  ggtitle("Evolution of conventionality") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge")

plot_simple_gen_cond


plot_simple_gen_cond_chain <- ggplot(df_conventionality, aes(Generation, Conventionality, fill = Condition)) +
  geom_bar(fun.y = "mean", stat = "summary", position = "dodge") +
  ggtitle("Evolution of conventionality") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge") +
  facet_wrap(df_conventionality$Chain)

plot_simple_gen_cond_chain




plot_simple_compl <- ggplot(SD, aes(Generation, Complexity, fill = Condition)) +
  geom_bar(fun.y = "mean", stat = "summary", position = "dodge") +
  ggtitle("Evolution of complexity") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge")

plot_simple_compl



plot_simple_compl_chain <- ggplot(all_data_w_all_conv_source, aes(Generation, Complexity, fill = Condition)) +
  geom_bar(fun.y = "mean", stat = "summary", position = "dodge") +
  ggtitle("Evolution of complexity") +
  stat_summary(geom = "errorbar", fun.data = mean_se, position = "dodge") +
  facet_wrap(all_data_w_all_conv_source$Chain)

plot_simple_compl_chain



# Error bars represent standard error of the mean
ggplot(df_conventionality, aes(x=Generation, y=Conventionality, fill=Condition)) + 
    geom_bar(position=position_dodge(), stat="identity") +
    geom_errorbar(aes(ymin=Conventionality-se, ymax=Conventionality+se),
                  width=.2,                    # Width of the error bars
                  position=position_dodge(.9))

df_conventionality$Generation <- as.factor(df_conventionality$Generation)






plot_simple_gen_cond1 <- ggplot(subset(df_conventionality, Condition == 1), aes(Generation, Conventionality)) +
                             geom_col()#geom_bar(stat = "identity")
  
plot_simple_gen_cond1

plot_simple_gen_cond2 <- ggplot(subset(df_conventionality, Condition == 2), aes(Generation, Conventionality)) +
                             geom_bar(stat = "identity")
plot_simple_gen_cond2

plot_simple_gen_cond3 <- ggplot(subset(df_conventionality, Condition == 3), aes(Generation, Conventionality)) +
                             geom_bar(stat = "identity")
plot_simple_gen_cond3


plot_simple_gen_cond4 <- ggplot(subset(df_conventionality, Condition == 4), aes(Generation, Conventionality)) +
                             geom_bar(stat = "identity")
plot_simple_gen_cond4




# source image and conventionality
plot_simple_gen_source <- ggplot(df_conventionality, aes(Source_image, Conventionality)) +
  geom_bar(stat = "identity")# +
  #geom_errorbar(aes(ymin=(Complexity-sd(Complexity)), ymax=(Complexity-sd(Complexity))), width=.2, position=position_dodge(.9))
plot_simple_gen_source

# participant and conventionality
plot_simple_subj <- ggplot(df_conventionality, aes(Subject, Conventionality)) +
                            geom_jitter()#geom_bar(stat = "identity")
plot_simple_subj

```
